---
title: "Milestone 4"
author: "Anan Hafez"
date: "10/10/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(janitor)
library(tidyr)
library(stringr)
library(httr)
library(RCurl)
library(lubridate)
library(readxl)
library(gt)
library(reshape2)
library(ggplot2)
library(purrr)
```


Hello! Thanks for coming back for Episode 4 of "Anan's Great R Journey". I've made solid progress on making my NBA data cleaner for use. For you, I created these two visualizations showing how the 3 point shot in basketball has grown on its own and relative to the other shot types. I'm very happy with these and definitely see at least one making into my final project. I hope you enjoy!

```{r}
nba_stats <- read.csv("nba_stats_clean_historic.csv") %>% clean_names() 

nba_stats %>% group_by(season) %>% summarize(total_shots = sum(fga), total_3p = sum(x3pa)) %>% mutate(prop_3p = round((total_3p/total_shots), digits = 2)) %>% ggplot(aes(x = season, y = prop_3p)) + geom_line() + labs(title = "How the 3-Point Shot grew in the NBA", x = "NBA Season", y = "Proportion of All Shots that were 3-Pointers") + scale_x_continuous(breaks = c(1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020))


```

```{r}
points_over_time <- nba_stats %>% group_by(season) %>% summarize(total_2points = sum(x2p * 2), total_3points = sum(x3p * 3), total_ft = sum(ft), total_points = (total_2points + total_3points + total_ft), prop_2points = total_2points/total_points, prop_3points = total_3points/total_points, prop_ft = total_ft/total_points) 

ggplot(points_over_time, aes(season)) + geom_line(aes(y = prop_2points, color = "var0")) + geom_line(aes(y = prop_3points, colour = "var1")) + geom_line(aes(y = prop_ft, colour = "var2")) + ylim(0,1) + scale_colour_manual(labels = c("2 Pointer", "3 Pointer", "Free Throw"), values = c("blue", "red", "green")) + scale_x_continuous(breaks = c(1980, 1985, 1990, 1995, 2000, 2005, 2010, 2015, 2020)) + labs(title = "Sources of NBA Points Over Time", y = "Percentage of Total Points", x = "NBA Season") + theme(legend.title = element_blank())

```



